\problemname{Adjoin the Networks}
\illustration{.4}{adjoin}{Wikimedia, cc-by-sa}

One day your boss explains to you that he has a bunch of computer networks
that are currently unreachable from each other, and he asks you,
the cable expert's assistant, to adjoin the networks to each other using new cables.
Existing cables in the network cannot be touched.

He has asked you to use as few cables as possible, but the length of
the cables used does not matter to him, since the cables are optical
and the connectors are the expensive parts. Your boss is rather picky
on cable usage, so you know that the already existing networks have as
few cables as possible.% without disconnecting already connected computers.

% Being a computer network wizard, you want to be promoted to a cable
% network expert's assistant. 
Due to your humongous knowledge of computer networks, you are of
course aware that the latency for an information packet travelling across
the network is proportional to the number of \emph{hops} the
packet needs, where a hop is a traversal along a single cable.
And since you believe a good solution to your boss' problem
may earn you that long wanted promotion, you decide to
minimise the maximum number of hops needed between any pair of
network nodes.

\section*{Input}
On the first line, you are given two positive integers, the number~$1 \leq c
\leq 10^5$
of computers and the number~$0 \leq \ell \leq c-1$ of existing cables. Then
follow~$\ell$ lines, each line consisting of two integers~$a$ and~$b$,
the two computers the cables connect. You may assume that every
computer has a unique name between~$0$ and~$n-1$.

\section*{Output}
The maximum number of hops in the resulting network.
